---
title       : Swirl with Slidify
author      : Ramnath Vaidyanathan
hitheme     : solarized_light
widgets     : [bootstrap, quiz, shiny, interactive]
mode        : selfcontained
--- #slide1

## Slide 1

Today, I'll be teaching you the basics of data analysis. It probably makes sense to start by defining the word DATA.

<script>
$(document).ready(function(){
  $('#slide1 article p').typewrite()
})
</script>

---

## Slide 2

Here is a diagram showing the relationship between a population and a sample.

```{r echo = F}
plot(0,xlim=c(-10,10),ylim=c(-10,10),type="n",xlab="",ylab="",bty="n",xaxt="n",yaxt="n", main="Population vs. Sample")
draw.circle(0,0,7,border="black",col="yellow")
draw.circle(3,0,3,border="black",col="red")
text(-3.5,0,"Population", font=2)
text(3,0,"Sample", font=2)
```

--- &radio

## Slide 3

Let's quickly test your understanding of the term REPRESENTATIVE. If you were interested in studying the health of men living in the US, ages 18-25, which sample would be more representative of the target population: a sample of 50 men who live in a nearby retirement home, or a sample of 50 men who are students at a local university?

1. Men living at the retirement home
2. _College students_

<div class="progress source">
  <div class="bar" style="width: 60%;"></div>
</div>

*** .hint

This is a hint

--- &interactive

## Slide 5

To illustrate these concepts, we will now look at a real life dataset. Type 'cars' and press Enter to see the dataset we'll be working with.

```{r opts.label = 'interactive', results = 'markup', eval = F, cache = F}
head(cars)
```

--- &submitcompare1

Mean, median, and mode are all measures of

--- &interactive

To illustrate these concepts, we will now look at a real life dataset. Type 'cars' and press Enter to see the dataset we'll be working with.

```{r opts.label = 'interactive', eval = F, cache = F}
cars
```

*** =hint

Type 'cars' and press Enter. Do not use quotes, spaces, or uppercase letters.






